The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}

### 2021-07-08 Draft.tex
Update

%\documentclass[12pt, a4paper]{article}
\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
% \usepackage{ngerman}
\usepackage[ansinew]{inputenc}
\usepackage[left=2.5cm,top=2.5cm]{geometry}

@@

\author{Lucas Laub\inst{1}\orcidID{6621331} \and
Second Author\inst{2}\orcidID{1111-2222-3333-4444}}

@@

\section{Introduction}
\section{Materials and Methodes}
\subsection{Preperations}
The experiment was conducted by creating a software implementing Fig.~\ref{fig1}.
This software allowed the tracking of {\itshape technical problems} introduced by
the software itself as well as the points and answers scored by each participant.
Additianaly a room with an adequat number of computers with a fiber-connection
to the server are needed, to rule out uncontrolled network problems.
Half of the cumputers are manipulated and simulate the network problems with the
use of the software.

@@

\section{Results}
\section{Discussion}
\section{Conclusion}
\section{Refernces}
\end{document}

>>>>

%\documentclass[12pt, a4paper]{article}
\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
% \usepackage{ngerman}
\usepackage[ansinew]{inputenc}
\usepackage[left=2.5cm,top=2.5cm]{geometry}

@@

\author{Lucas Laub\inst{1}\orcidID{6621331} \and
Alexander Perekhrest \inst{2}\orcidID{6379748}}

@@

\section{Introduction}
When trying to transfer an already existing method on a relatively new platform, 
it's important to know the things that come with being on such a platform and the 
possible influences those things might have on the method.\\\\

In day-to-day usage of online platforms and services it's not uncommon to face some 
issues, whether it's execution, connectivity and so on. E-Learning-platforms are not 
particularly different to those. Therefore, we want to discuss, in this paper, to 
which extent these problems can influence the test-results of being on such an 
'issue-infected' platform in contrast to a well running platform with no issues.\\\\

We tried to focus on the most frequent issues we faced in our experience of browsing 
on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\

\section{Materials and Methodes}
\subsection{Preperations}
The experiment was conducted by creating a software implementing Fig.~\ref{fig1}.
This software allowed the tracking of {\itshape technical problems} introduced by
the software itself as well as the points and answers scored by each participant.
Additianaly a room with an adequat number of computers with a fiber-connection
to the server are needed, to rule out uncontrolled network problems.
Half of the cumputers are manipulated and simulate the network problems with the
use of the software.

@@

\newpage
\section{Results}
The results are displayed in chronological order of the analysis, there is
no emphisis on the significans given by the order itself.

\subsection{Controll Group vs Error Group}
\begin{figure}
    \begin{minipage}{0.45\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the controll group (50f/50m) and
        the error group (50f/50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig2}
    \end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the controll group (50f/50m) the error group (50f/50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & controll group & error group \\
        \hline
        median & 53.0&43.5 \\
        \hline
        standart deviation & 29.278&29.826 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.728} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.467} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Controll Group Female vs Error Group Female}
\begin{figure}
    \begin{minipage}{0.45\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the controll group (50f) and
        the error group (50f).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig3}
    \end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the controll group (50f) the error group (50f).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & controll group & error group \\
        \hline
        median & 55.5&40.0 \\
        \hline
        standart deviation & 27.85&30.933 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.949} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.345} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Controll Group Male vs Error Group Male }
\begin{figure}
    \begin{minipage}{0.45\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the controll group (50m) and
        the error group (50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig4}
    \end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the controll group (50m) the error group (50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & controll group & error group \\
        \hline
        median & 52.5&50.5 \\
        \hline
        standart deviation & 30.638&28.495 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.08} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.936} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Controll Group vs Error Group}
\begin{figure}
    \begin{minipage}{0.45\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the controll group (50f) and
        the controll group (50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig5}
    \end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the controll group (50f) the controll group (50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & controll group(f) & controll group(m) \\
        \hline
        median & 55.5&52.5 \\
        \hline
        standart deviation & 27.85&30.638 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.101} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.919} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Controll Group vs Error Group}
\begin{figure}
    \begin{minipage}{0.45\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the error group (50f) and
        the error group (50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig6}
    \end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the error group (50f) the error group (50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & error group & error group \\
        \hline
        median & 40.0&50.5 \\
        \hline
        standart deviation & 30.933&28.495 \\
        \hline
        t-value & \multicolumn{2}{c|}{- 0.759} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.45} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Controll Group vs Error Group}
\begin{figure}
    \begin{minipage}{0.45\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the controll group (50f) and
        the error group (50m).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig7}
    \end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the controll group (50f) the error group (50m).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & controll group & error group \\
        \hline
        median & 55.5&50.5 \\
        \hline
        standart deviation & 27.85&28.495 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.19} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.85} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\subsection{Controll Group vs Error Group}
\begin{figure}
    \begin{minipage}{0.45\textwidth}        
        \includegraphics[width=\textwidth]{code/generate/all.png}
        \caption{The colored squares in the boxplot displays
        the upper and lower quartile of points earned by the controll group (50m) and
        the error group (50f).The green line marks the mean of all datapoints in the group.
        The gray line marks the median  of the given group.} \label{fig8}
    \end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
\captionof{table}{The calculated median, standart deviation and t, p-values
    for the controll group (50m) the error group (50f).
    The t,p-values were calculated by using a two-sided t-test.}
\begin{tabular}[]{| c | c | c |}
        \hline
        & controll group & error group \\
        \hline
        median & 52.5&40.0 \\
        \hline
        standart deviation & 30.638&30.933 \\
        \hline
        t-value & \multicolumn{2}{c|}{0.81} \\
        \hline
        p-value & \multicolumn{2}{c|}{0.42} \\
        \hline            
\end{tabular}
\end{minipage}
\end{figure}

\section{Discussion}
\section{Conclusion}
\section{Refernces}
\end{document}
